Self Regulation Ontology Retest Data Report

### 2017-11-02 code/Lit_Review_Figure.Rmd
cont working on new report

```{r warning= FALSE, message =FALSE, fig.height=36, echo=FALSE, eval=FALSE}
fig_data %>%
  mutate(dv = factor(dv, levels = dv[order(task)]),
         days_cutoff = ifelse(days < 60, days, 120),
         days = paste(days, '; reference:', reference)) %>%
ggplot(aes(x = dv, y = retest_reliability, label=days))+
  geom_point(aes(color = task, size=sample_size, shape = type, alpha = days_cutoff))+
  coord_flip()+
  theme_bw()
```

>>>>

```{r warning= FALSE, message =FALSE, fig.height=36, echo=FALSE, eval=FALSE}
#Static plot with everything in same panel
fig_data %>%
  mutate(dv = factor(dv, levels = dv[order(task)]),
         days_cutoff = ifelse(days < 60, days, 120),
         days = paste(days, '; reference:', reference)) %>%
ggplot(aes(x = dv, y = retest_reliability, label=days))+
  geom_point(aes(color = task, size=sample_size, shape = type, alpha = days_cutoff))+
  coord_flip()+
  theme_bw()
```

### 2017-11-02 code/SRO_Report.Rmd
began updating report with new data releases
cont working on new report

```{r, message=FALSE, warning=FALSE, include=FALSE}
library(dplyr)
library(tidyr)
library(ggplot2)
library(gridExtra)
library(lme4)
library(GGally)
library(jsonlite)
library(psych)
library(rmarkdown)
library(psych)
library(stringr)
library(plotly)
library(DT)
sem <- function(x) {sd(x, na.rm=T) / sqrt(length(x))}
render_this <- function(){rmarkdown::render('SRO_Report.Rmd', output_dir = '../output', html_notebook(toc = T, toc_float = T, code_folding = 'hide'))}
options(scipen = 1, digits = 4)
```

@@

This sample consists of data for 150 subjects of the original sample of 522 that has completed the initial battery of 37 cognitive tasks, 23 surveys and 3 surveys on demographics. Details of the original sample as well as quality control (qc) procedures are described elsewhere. Invited participants were chosen randomly and only subsets of them were invited for a given batch (instead of opening the battery to all qualified subjects) with the intention to avoid a potential oversampling and bias towards "high self regulators".

@@

>>>>

```{r, message=FALSE, warning=FALSE, include=FALSE}
library(dplyr)
library(tidyr)
library(ggplot2)
library(gridExtra)
library(lme4)
library(GGally)
library(jsonlite)
library(psych)
library(rmarkdown)
library(psych)
library(stringr)
library(plotly)
library(DT)
sem <- function(x) {sd(x, na.rm=T) / sqrt(length(x))}
g_legend<-function(a.gplot){
  tmp <- ggplot_gtable(ggplot_build(a.gplot))
  leg <- which(sapply(tmp$grobs, function(x) x$name) == "guide-box")
  legend <- tmp$grobs[[leg]]
  return(legend)}
render_this <- function(){rmarkdown::render('SRO_Report.Rmd', output_dir = '/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/reports', html_notebook(toc = T, toc_float = T, code_folding = 'hide'))}
options(scipen = 1, digits = 4)
```

@@

This sample consists of data for 150 subjects of the original sample of 522 that has completed the initial battery of 37 cognitive tasks, 23 surveys and 3 surveys on demographics. Details of the original sample as well as quality control (qc) procedures are described elsewhere (Eisenberg et al., 2017). Invited participants were chosen randomly and only subsets of them were invited for a given batch (instead of opening the battery to all qualified subjects) with the intention to avoid a potential oversampling and bias towards "high self regulators".

@@

One the major contributions of this project is a comprehensive literature review of the retest reliabilities of the surveys and tasks that were used. We reviewed the literature on a measure (as opposed to task level) paying attention to differences in sample size, the delay between the two measurements as well as the statistic that was used to assess reliabilities (e.g. Spearman vs. Pearson correlations). Here we present a table and a visualization summarizing our findings. References mentioned in the table below can be found [here](https://docs.google.com/spreadsheets/d/1hcED4_rWSGSE8Td0aqT0kWqlLCBAzRNKBXj3tSram58/edit?usp=sharing).

```{r}
lit_review <- read.csv('/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/input/lit_review_figure.csv')

datatable(lit_review %>%
  mutate(dv = gsub(".ReflogTr", "",dv),
         dv = gsub(".logTr", "", dv)))
```

Measure level plot

```{r warning=FALSE, message=FALSE}
lit_review = lit_review %>%
  separate(dv, c("task_group", "var"), sep="\\.",remove=FALSE,extra="merge") %>%
  mutate(task_group = factor(task_group, levels = task_group[order(task)]),
         raw1_fit0 = grepl('raw', variable_type),
         type = as.character(type)) %>%
  mutate(task_group = gsub("_", " ", task_group),
         var = gsub("_", " ", var),
         dv = gsub(".ReflogTr", "",dv),
         dv = gsub(".logTr", "", dv)) %>%
  arrange(task_group, raw1_fit0, var) %>%
  mutate(task_group = ifelse(task_group == "psychological refractory period two choices", "psychological refractory period", ifelse(task_group == "angling risk task always sunny", "angling risk task",task_group))) %>%
  mutate(task_group = gsub("survey", "", task_group)) %>%
    select(-measure_description, -reference)
```

```{r warning= FALSE, message =FALSE, echo=FALSE}
p1_legend = lit_review %>%
  filter(task == 'task') %>%
ggplot(aes(y = var, x = retest_reliability)) + 
  geom_point(aes(size=sample_size, shape=type))+
  facet_grid(task_group~., switch = "y", scales = "free_y", space = "free_y") +
  theme(panel.spacing = unit(0.5, "lines"), 
        strip.placement = "outside",
        strip.text.y = element_text(angle=180),
        panel.background = element_rect(fill = NA),
        panel.grid.major = element_line(colour = "grey80"),
        legend.position = 'bottom') + 
  xlab("")+
  ylab("")+
  scale_x_continuous(limits = c(-0.25,1), breaks=c(-0.25, 0, 0.25, 0.5, 0.75, 1))+
  scale_shape_manual(breaks = sort(lit_review$type), values = c(15, 16, 17, 3))

p1 = lit_review %>%
  filter(task == 'task') %>%
ggplot(aes(y = var, x = retest_reliability)) + 
  geom_point(aes(size=sample_size, shape = type), color='#00BFC4')+
  facet_grid(task_group~., switch = "y", scales = "free_y", space = "free_y") +
  theme(panel.spacing = unit(0.5, "lines"), 
        strip.placement = "outside",
        strip.text.y = element_text(angle=180),
        panel.background = element_rect(fill = NA),
        panel.grid.major = element_line(colour = "grey80"),
        legend.position = 'bottom') + 
  xlab("")+
  ylab("")+
  scale_x_continuous(limits = c(-0.25,1), breaks=c(-0.25, 0, 0.25, 0.5, 0.75, 1))+
  scale_shape_manual(breaks = sort(lit_review$type), values = c(15, 16, 17, 3))

p2 = lit_review %>%
  filter(task == 'survey') %>%
ggplot(aes(y = var, x = retest_reliability)) + 
  geom_point(aes(size=sample_size, shape = type), color = '#F8766D')+
  facet_grid(task_group~., switch = "y", scales = "free_y", space = "free_y") +
  theme(panel.spacing = unit(0.5, "lines"), 
        strip.placement = "outside",
        strip.text.y = element_text(angle=180),
        panel.background = element_rect(fill = NA),
        panel.grid.major = element_line(colour = "grey80")) + 
  xlab("")+
  ylab("")+
  scale_x_continuous(limits = c(-0.25,1), breaks=c(-0.25, 0, 0.25, 0.5, 0.75, 1))+
  scale_shape_manual(breaks = sort(lit_review$type), values = c(15, 17, 3))

mylegend<-g_legend(p1_legend)

ggsave('Lit_Review_Plot.jpg', plot = p3, device = "jpeg", path = "/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/figures/", width = 24, height = 20, units = "in")
rm(p1, p2, p3, p1_legend, mylegend)
```

```{r echo=FALSE, out.width='100%'}
knitr::include_graphics('/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/figures/Lit_Review_Plot.jpg')
```

Because this plot is difficult to digest we summarize it on a task level to give a general sense of the main takeaways. This plot naturally disregards much of the fine grained information.

```{r}
p1_t <- lit_review %>%
  filter(task == 'task') %>%
ggplot(aes(y = factor(task_group, levels=rev(unique(task_group))), x = retest_reliability)) + 
  geom_point(aes(size=sample_size, shape = type), color='#00BFC4')+
  theme_bw()+
  theme(axis.text.y = element_text(size=43),
        legend.position = 'none') + 
  xlab("")+
  ylab("")+
  scale_x_continuous(limits = c(-0.25,1), breaks=c(-0.25, 0, 0.25, 0.5, 0.75, 1))+
  scale_y_discrete(labels = function(x) str_wrap(x, width = 10))+
  scale_shape_manual(breaks = sort(lit_review$type), values = c(15, 16, 17, 3))+
  scale_size_continuous(range = c(5, 50))+
  geom_vline(xintercept = 0, color = "red", size = 1)

p2_t <- lit_review %>%
  filter(task == 'survey') %>%
ggplot(aes(y = factor(task_group, levels=rev(unique(task_group))), x = retest_reliability)) + 
  geom_point(aes(size=sample_size, shape = type), color='#F8766D')+
  theme_bw()+
  theme(axis.text.y = element_text(size=43),
        legend.position = 'none') + 
  xlab("")+
  ylab("")+
  scale_x_continuous(limits = c(-0.25,1), breaks=c(-0.25, 0, 0.25, 0.5, 0.75, 1))+
  scale_y_discrete(labels = function(x) str_wrap(x, width = 10))+
  scale_shape_manual(breaks = sort(lit_review$type), values = c(15, 16, 17, 3))+
  scale_size_continuous(range = c(5, 50))+
  geom_vline(xintercept = 0, color = "red", size = 1)

p3_t <- arrangeGrob(p1_t, p2_t, nrow=1)

ggsave('Lit_Review_Plot_t.jpg', plot = p3_t, device = "jpeg", path = "/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/figures/", width = 27, height = 48, units = "in", limitsize = FALSE)
rm(p1_t, p2_t, p3_t)
```

```{r echo=FALSE, out.width='100%'}
knitr::include_graphics('/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/figures/Lit_Review_Plot_t.jpg')
```

An interactive version of this plot could be find [here](https://zenkavi.github.io/SRO_Retest_Analyses/output/reports/Lit_Review_Figure.html)

Takeaways from this review are: 
- Survey measures have been reported to higher reliability compared to task measures  
- Survey measures have less variability in the reported reliabiltiy estimates compared to task measures'
